### 2018-08-06 article.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[2-Category]
A \emph{strict} 2-category \catC is a category \emph{enriched over \textbf{Cat}}, the category of categories.

\begin{itemize}
\item objects are natural number $\mathbb{N}$, called \emph{0-cells}
\item for all 0-cells $(a, b)$, a category $\catC(a, b)$ with
\begin{itemize}
\item objects $f: a \to b$, called \emph{1-cells}
\item morphisms are called \emph{2-cells}
\item for all 2-cells $r: f \Rightarrow g$ and $s: g \Rightarrow h$, a composition operator $r \bullet s: f \Rightarrow h$ called \emph{vertical composition}
\end{itemize}
\item for all 0-cells $a$ and all 1-cells $f: a \to a \in \catC(a, a)$, there is an identity 2-cell $r: f \Rightarrow f$, written $Id_f$
\item for all 0-cells $(a, b, c)$ a bifunctor $\circ: \catC(b, c) \times \catC(a, b) \to \catC(a, c)$ called \emph{horizontal composition}
\end{itemize}

In the following we'll always write $a, b, c$ for \emph{0-cells}, $f, g, h$ for \emph{1-cells} and $r, s, t$ for \emph{2-cells}.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Monoidal 2-category]
A \emph{strict} monoidal 2-category $(\catC, \otimes)$ is a strict 2-category with

\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Because $\circ$ and $\otimes$ are bifunctor, for all 0-cells $a, b \in \catC$ and all 2-cells $r, s, t, u \in \catC(a, b)$

\begin{align}
(r \circ s) \bullet (t \circ u) &= (r \bullet t) \circ (s \bullet u) \cr
(r \otimes s) \bullet (t \otimes u) &= (r \bullet t) \otimes (s \bullet u)
\end{align}
\end{remark}

@@

>>>>

We assume that the reader is familiar with the notion of symmetric
monoidal category; a standard reference is
\cite{MacLane:CatsWM:1971}.

\begin{definition}\label{def:PROP}
  A \emph{PROP} is strict symmetric monoidal category whose objects
  are the natural numbers, and where the action of the tensor product on
  objects is given by addition.
\end{definition}

PROPs have been used to formalise many algebraic structures
\cite{Lack:2004sf}, however our interest here is to formalise a
general notion of \emph{circuit} as a free PROP over a certain set of
gates.

\begin{example}  \label{ex:boolean-circs}
  TODO -- boolean circuits
\end{example}

\begin{example}  \label{ex:quantum-circs}
  TODO -- quanutm circuits
\end{example}

\begin{example}  \label{ex:zx-calculus}
  TODO -- zx-calculus
\end{example}

\noindent
Note that all of these examples usually include an equational theory.
We will don't include these equations in the  definition since we will
model them as higher dimensional arrows.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{definition}  \label{def:strict-two-cat}
A \emph{strict} 2-category \catC is a category \emph{enriched over
  \textbf{Cat}}, the category of categories, \emph{viz:}
\begin{itemize}
\item A category \catC, whose objects and arrows are known as
  0-cells and 1-cells respectively.
\item For every pair of objects $A$ and $B$, we have a
  category $\catC(A, B)$, whose arrows are known as 2-cells.
\item For 2-cells $\alpha : f \Rightarrow g$ and $\beta : g
  \Rightarrow h$ in $\catC(A,B)$ their (vertical) composite is denoted
  $\beta\bullet\alpha : f \Rightarrow h$.
\item For every 1-cell $f:A\to B$ we denote its identity 2-cell by
  $Id_f:f \Rightarrow f$.
\item For all 0-cells $a$, $b$, $c$ a bifunctor $\circ: \catC(b, c)
  \times \catC(a, b) \to \catC(a, c)$ called \emph{horizontal
    composition} of 2-cells.
\end{itemize}
\REM{Need here the name for a 2-cat with all 2-cells invertible;  the
  term 2-groupoid refers to the case where both 1- and 2-cells are
  invertible.}
\end{definition}

\noindent
In the following we'll always write $A, B, C$ for \emph{0-cells}, $f,
g, h$ for \emph{1-cells} and $\alpha$, $\beta$, $\gamma$ for
\emph{2-cells}.

\begin{definition}
  \label{def:two-functor}
  DEFINITION OF 2-FUNCTOR here
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{definition}\label{def:monoidal-two-cat}
A \emph{strict} monoidal 2-category $(\catC, \otimes)$ is a strict
2-category with
\REM{Is this \emph{required}?  Doesn't it follow from the  definition
  of bifunctor?  (It does in the 1-category case, so it should do
  here!)}
\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that
  on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\REM{This definition doesn't quite work without the additoin type
  information on the 2-cells}
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Since $\circ$ and $\otimes$ are bifunctorial, we have the following
interchange equations for all 0-cells $A, B \in \catC$ and all 2-cells $r, s, t, u \in \catC(A, B)$
\begin{align}
(r \circ s) \bullet (t \circ u) &= (r \bullet t) \circ (s \bullet u) \\
(r \otimes s) \bullet (t \otimes u) &= (r \bullet t) \otimes (s \bullet u)
\end{align}
\end{remark}

@@

\section{Quantale Enriched Categories}
\label{sec:quant-enrich-categ}
